# Installation

## Development Version

Install the development version from GitHub:

```{r install-github, eval=FALSE}
install.packages("devtools")
devtools::install_github("iqb-research/eatAutoCode")
```

Then load the package:

```{r load-package, eval=FALSE}
library(eatAutoCode)
```

## Local Development Checkout

If you are working from a local clone of the repository, install the package dependencies and load the package with `devtools`:

```{r local-load, eval=FALSE}
install.packages("devtools")
devtools::load_all(".")
```

The package wraps JavaScript code shipped in `inst/index.js`. If the JavaScript dependencies are updated, rebuild the bundled auto-coder before testing the package:

```{r update-js, eval=FALSE}
packer::npm_install()
packer::npm_install("@iqb/responses")
```

After updating the JavaScript bundle, run the tests:

```{r test-package, eval=FALSE}
devtools::test()
```

## Rendering This Book

The documentation is a bookdown project that renders into the `docs/` directory:

```{r render-book, eval=FALSE}
bookdown::render_book("index.Rmd")
```

The `docs/` directory can be used as the source folder for GitHub Pages.

