# Workflows

## Coding One Response Object

Use `code_responses()` when you have one coding scheme and one response object for a unit.

```{r code-one, eval=FALSE}
library(eatAutoCode)

coding_scheme <- jsonlite::read_json("coding-scheme.json")
responses <- jsonlite::read_json("responses.json")

coded <- code_responses(
  coding_scheme = coding_scheme,
  responses = responses
)

coded
```

The result is a data frame with one row per coded variable. The usual columns are:

- `id`: variable identifier from the coding scheme,
- `status`: coding status,
- `value`: response value used for coding,
- `key`: matching key, when available,
- `code`: assigned code, and
- `score`: assigned score.

## Coding With Manual Overrides

Manual coding data can be supplied to add or overwrite codes. This is useful when individual responses have already been scored by hand or need to be forced to a specific code.

```{r code-manual, eval=FALSE}
manual_codes <- list(
  list(id = "b1", status = "CODING_COMPLETE", code = 31, score = 1),
  list(id = "b2", status = "CODING_COMPLETE", code = -99, score = 0)
)

coded <- code_responses(
  coding_scheme = coding_scheme,
  responses = responses,
  manual = manual_codes
)
```

## Coding Multiple Response Objects

Use `code_responses_array()` when the same coding scheme should be applied to multiple response objects.

```{r code-array, eval=FALSE}
response_array <- list(
  list(unit_key = "A1", responses = responses),
  list(unit_key = "A2", responses = responses),
  list(unit_key = "A3", responses = responses)
)

coded_array <- code_responses_array(
  coding_scheme = coding_scheme,
  responses = response_array
)

coded_array
```

The returned data frame includes `unit_key`, so coded rows can be traced back to the original response object.

## Handling List Values and Missing Values

`code_responses_array()` and `extract_variable_location()` coerce list-like values to character values. By default, list values are wrapped with `[[[` and `]]]` and collapsed with `;;;`.

```{r code-array-options, eval=FALSE}
coded_array <- code_responses_array(
  coding_scheme = coding_scheme,
  responses = response_array,
  collapse = ";;;",
  wrap_start = "[[[",
  wrap_end = "]]]",
  missing = "___MISSING___"
)
```

The `missing` placeholder is transformed to `NA` in the returned data frame.

## Inspecting Dependencies

Coding schemes can contain variables that depend on other variables. Use `get_dependency_tree()` to inspect this structure before coding or debugging a coding scheme.

```{r dependency-tree, eval=FALSE}
dependency_tree <- get_dependency_tree(coding_scheme)
dependency_tree
```

The result includes the variable `id`, its dependency `level`, its `sources`, and the `page`.

## Extracting Variable Locations

Use `extract_variable_location()` with unit definitions that contain a `definition` column. Because this operation is memory-consuming, process small batches of unit definitions.

```{r variable-location, eval=FALSE}
units <- tibble::tibble(
  unit_key = c("unit_01", "unit_02"),
  definition = c(unit_definition_json_01, unit_definition_json_02)
)

locations <- extract_variable_location(units)
locations
```

For large exports, split the units into batches before calling the function.

