# Function Reference

## `code_responses()`

```{r ref-code-responses, eval=FALSE}
code_responses(coding_scheme, responses, manual = "null")
```

Codes one response object with one coding scheme.

Arguments:

- `coding_scheme`: list or character string containing a coding scheme from IQB Studio Lite.
- `responses`: list or character string containing unit responses from IQB Testcenter.
- `manual`: optional list or character string with manual codes. The default `"null"` is treated like missing manual data.

Returns a data frame.

## `code_responses_array()`

```{r ref-code-responses-array, eval=FALSE}
code_responses_array(
  coding_scheme,
  responses,
  collapse = ";;;",
  wrap_start = "[[[",
  wrap_end = "]]]",
  missing = "___MISSING___"
)
```

Codes several response objects with one coding scheme.

Arguments:

- `coding_scheme`: list or character string containing a coding scheme from IQB Studio Lite.
- `responses`: list or character string containing an array of response objects.
- `collapse`: separator for concatenating list values.
- `wrap_start`: prefix used when wrapping list values.
- `wrap_end`: suffix used when wrapping list values.
- `missing`: placeholder that is converted to `NA`.

Returns a data frame. The `value` column is coerced to character, so list entries can be represented in a rectangular table.

## `get_dependency_tree()`

```{r ref-dependency-tree, eval=FALSE}
get_dependency_tree(coding_scheme)
```

Displays the variable dependency tree of a coding scheme.

Arguments:

- `coding_scheme`: list or character string containing a coding scheme from IQB Studio Lite.

Returns a data frame with dependency information.

## `extract_variable_location()`

```{r ref-variable-location, eval=FALSE}
extract_variable_location(
  units,
  collapse = ";;;",
  wrap_start = "[[[",
  wrap_end = "]]]",
  missing = "___MISSING___"
)
```

Extracts variable locations from unit definitions.

Arguments:

- `units`: tibble with a `definition` column containing unit definitions.
- `collapse`: separator for concatenating list values.
- `wrap_start`: prefix used when wrapping list values.
- `wrap_end`: suffix used when wrapping list values.
- `missing`: placeholder that is converted to `NA`.

Returns a data frame.

