# Development

## Repository Layout

Important paths in the repository:

- `R/`: R wrapper functions exported by the package.
- `srcjs/`: TypeScript and JavaScript source code for the auto-coder bridge.
- `inst/index.js`: bundled JavaScript shipped with the R package.
- `tests/testthat/`: package tests and test fixtures.
- `man/`: generated R documentation.
- `docs/`: rendered bookdown site.

## Updating Documentation

Function documentation is written in roxygen comments in the `R/` files. After editing those comments, regenerate the manual pages and namespace:

```{r document-package, eval=FALSE}
devtools::document()
```

The bookdown pages are written in the top-level `.Rmd` files listed in `_bookdown.yml`. Render the book after editing pages:

```{r render-development, eval=FALSE}
bookdown::render_book("index.Rmd")
```

## Testing

Run the package tests after changes to the R wrappers or JavaScript bundle:

```{r run-tests, eval=FALSE}
devtools::test()
```

The tests include examples for:

- coding one response object,
- coding arrays of response objects,
- applying manual coding data, and
- inspecting dependency trees.

## Publishing With GitHub Pages

This book is configured to render into `docs/`. In the GitHub repository settings, set Pages to publish from the `docs/` folder on the `main` branch.

